Heuristics and Really Hard Instances for Subgraph Isomorphism Problems

### 2015-12-23 paper/paper.tex
IJCAI 16
More
Betterer titles

\usepackage{ijcai13}
\usepackage{times}
\usepackage{complexity}
\usepackage{microtype}
\usepackage{gnuplot-lua-tikz}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{placeins}
\usepackage{cleveref}
\usepackage{natbib}
\usepackage{dblfloatfix}

@@

\title{Really Hard Instances for the Subgraph Isomorphism Problem}
\author{Ciaran McCreesh\thanks{This work was supported by the Engineering and Physical Sciences
    Research Council [grant number EP/K503058/1]} \and Patrick Prossser \and James Trimble \\
University of Glasgow, Glasgow, Scotland \\
c.mccreesh.1@research.gla.ac.uk}

@@

\begin{abstract}
    We show how to generate ``really hard'' random instances for variants of the subgraph
    isomorphism problem. For the non-induced variant of the problem, we predict and observe a phase
    transition between satisfiable and unsatisfiable instances, with a corresponding complexity peak
    seen in three different solvers. For the induced variant of the problem, the behaviour is more
    complicated, with two phase transitions and an unexpectedly hard region in between. We show that
    this region remains hard when using pseudo-boolean and mixed integer encodings, and under
    reduction to the clique problem.
\end{abstract}

@@

\begin{figure}[tb]
    \input{gen-graph-phase-transition-bands.tex}
    \caption{The location of the phase transition, as the pattern grows. Shown are points where
    between 20\% and 80\% of instances are satisfiable.}
    \label{figure:phase-transition-bands}
\end{figure}

\subsection{Locating the Phase Transition}

@@

>>>>

\usepackage{ijcai16}
\usepackage{times}
\usepackage{complexity}
\usepackage{microtype}
\usepackage{gnuplot-lua-tikz}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{placeins}
\usepackage{cleveref}
\usepackage{natbib}
\usepackage{dblfloatfix}

@@

\title{Heuristics and Really Hard Instances for Subgraph Isomorphism Problems}
\author{Ciaran McCreesh\thanks{This work was supported by the Engineering and Physical Sciences
    Research Council [grant number EP/K503058/1]} \and Patrick Prossser \and James Trimble \\
University of Glasgow, Glasgow, Scotland \\
c.mccreesh.1@research.gla.ac.uk}

@@

\begin{abstract}
    We show how to generate ``really hard'' random instances for variants of the subgraph
    isomorphism problem. For the non-induced variant of the problem, we predict and observe a phase
    transition between satisfiable and unsatisfiable instances, with a corresponding complexity peak
    seen in three different solvers. For the induced variant of the problem, the behaviour is more
    complicated, with two phase transitions and an unexpectedly hard region in between. We show that
    this region remains hard when using pseudo-boolean and mixed integer encodings, and under
    reduction to the clique problem. Finally, we show that existing heuristics for the non-induced
    variant can be recovered by determining how to maximise the expected number of solutions, and
    that this technique gives new, better heuristics for the induced variant.
\end{abstract}

@@

\begin{figure}[tb]
    \input{gen-graph-phase-transition-bands.tex}
    \caption{The location of the phase transition, as the pattern grows. Shown are points where
    between 20\% and 80\% of instances are satisfiable. ?? Can we put predictions on here too?}
    \label{figure:phase-transition-bands}
\end{figure}

\subsection{Locating the Phase Transition, and Heuristics}

@@

\subsection{New Heuristics}
